Viscous Erosion in Porous Media

### 2018-03-26 docs/methods/erosion_methods.tex
small edits to methods paper

To simulate multiple bodies, it is essential to resolve the nonlocal
effects between the different bodies.  In this work, these interactions
are included with high-order accuracy by using an integral equation
method.  Integral equations have been used extensively to simulate
viscous fluids in complex geometries.  One particular application are
particulate flows, such as bubbles or droplets, and the classic book of
Pozrikidis~\cite{poz1992} describes BIEs for such problems.  For nearly
touching bodies, the quadrature associated with discretizing a BIE can
lead to instabilities of specialized quadrature is not applied.  Since
our bodies do not move, we are able to use upsampling, but future work
will require a near-singular integration scheme~\cite{qua-bir2014a,
klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

@@

\todo[inline]{paper of Bryan, Eric, and Pieter and one with Pietro,
George, and Ruben}

>>>>

To simulate multiple bodies, it is essential to resolve the nonlocal
effects between the different bodies.  In this work, these interactions
are included with high-order accuracy by using an integral equation
method~\cite{poz1992}.  Integral equations have been used extensively to
simulate viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  For nearly
touching bodies, the quadrature associated with discretizing a BIE can
lead to instabilities of specialized quadrature is not applied.  Since
our bodies do not move, we are able to use upsampling, but future work
will require a near-singular integration scheme~\cite{qua-bir2014a,
klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

@@
